Forecasting the Changing Dynamics of US Energy Product Exports to OECD Markets: The Role of the Russian-Ukraine Conflict and Future Scenarios

### 2023-05-18 report_Tomo editinta.Rmd
paeditinta

@@

addi_fc %>% 
  autoplot(
    crude_oil_bx) +
  labs(
    y = "Thousand Barrels",
    title = "Forecasts for U.S. Crude oil exports to OECD Europe") +
  guides(colour = guide_legend(title = "Forecast"))
```

>>>>

rel_rusoil <- rel_rusoil %>% 
  mutate(`Total Oil Imports from Russia / Total Oil Imports (%)` = gsub("%", "", `Total Oil Imports from Russia / Total Oil Imports (%)`)) %>% 
  select(Date, Country, `Total Oil Imports from Russia / Total Oil Imports (%)`)

@@

addi_fc %>% 
  autoplot(
    crude_oil_bx) +
  labs(
    y = "Thousand Barrels",
    title = "Forecasts for U.S. Crude oil exports to OECD Europe") +
  guides(colour = guide_legend(title = "Forecast"))

ggplot(oecd_relrus, aes(x = Date)) +
  geom_line(aes(y = "Total Oil Imports from Russia / Total Oil Imports (%)")) +
  ylab("Percentage") +
  ggtitle("Reliance on Russia") 
oecd_relrus
```
